---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OpenTrack

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Welcome to OpenTrack, an open-source platform for extracting training load variables from IMU data. The initial OpenTrack release can be used with triaxial accelerometer or 9-axis IMU data, and is functional with a single central device, and/or two devices corresponding to left and right limbs.

The current version of OpenTrack outputs impact counts and magnitudes, jump counts and heights, PlayerLoad, and other common training load variables, as well as both raw and processed time-series for each device. It is also designed to work with both .csv and SQL databases, which can be edited from within the platform.

## Installation

OpenTrack is tricky to install, probably because I haven't built the package properly. If you know how to make it so all the dependencies install automatically, feel free to contact me and tell me how...

To run OpenTrack, you will need to 
  1) make a copy of this repository in your system's 'R' folder
  2) install the dependencies 
  3) download and install the package

1) make a copy of this repository in your system's 'R' folder
Click the green button at the top of this page, download a zip. Once it's downloaded, right click and extract all to your system's R folder, normally in C:/Users/yourname_/Documents/R

2) install the dependencies
Click ctrl + shift + B. This won't work, but it seems the easiest way to install RTools.

Once it's done, run this code:
 
``` r
#install.packages("devtools")
devtools::install_version("shinydashboardPlus", version = "0.7.5", repos = "http://cran.us.r-project.org")
devtools::install_github("cvarrichio/rowr")
devtools::install_github("wleepang/shiny-directory-input")
install.packages("tidyverse")

```

3) download and install the package
Once they've installed, run this code:

``` r
#install.packages("devtools")
devtools::install_github("joseph-shaw/OpenTrack")
```
Alternatively, at this point you can just build the package yourself.

If you encounter an error regarding functions exported from shinydashboardPlus, just remove the current installation of shinydashboardPlus and reinstall as above (you may have to delete the folder from your package library).

If you want to use SQL, there's (going to be) a template of the database required in this repo.

You will also need to alter several of the files within the settings folder ("~ R/OpenTrack/settings") before you get started.

 - athletes.csv:       This file houses data about each athlete. You can edit to this directly, or do so through the 'Add athlete' tab in the "Analyse Data" page in the app.
 
 - sql.csv:            This file is used to create a SQL connection, or tell the app to use csv files instead (set the 'csv' cell to 0). To set up a SQL connection, add in the database information in each cell. You'll be prompted to enter the password each time you open the app (entry box in the r studio window; nothing will work until this is entered correctly). You can add a password permanently in the 'app_server.R' file instead.

 - lists.csv:          You can use this file to change the session type options in the drop down on the 'Analyse Data' page.
 
 - filepaths.csv:      You will need to change these if you want to edit where the app can look for files. Simply enter the filepaths and a name for the location you want to use.
 
 - export.csv:         This file can be used to change the data that is exported. Simply delete a column to remove it from the export.


Once installed, you can run the app with:

```{r example}
#library(OpenTrack)
#run_app()
#or
#OpenTrack::run_app()
```

## Using OpenTrack

OpenTrack currently has four tabs. When you open the app you'll start at the data upload page. Here you will need to upload the data from your IMU(s). There are upload tabs for central/left/right devices. If you click these and the file browser isn't populating, you either haven't set the filepaths in 'filepaths.csv' or you're using SQL and you haven't logged in. Here you will also need to set the date/time the devices were turned on, the units of time that your device outputs, and if your vertical axis is flipped. 

A couple of things to note here:
- There's not currently a function to sync the three devices, so if the times are out of sync, the data will be out of sync
- The time unit is currently 'time since turned on', and not a date-time unit. I'll probably look to add this in if there's demand for it

Once you've uploaded the data and changed your settings, hit the 'Process' button and move to the 'Analyse Data' tab. After it loads you'll find plots of the central device (plot tab 1) and L/R devices (plot tab 2). You'll also find data inputs for details about the session, or space to add a new athlete to the database.


















